Scottish Child Poverty Briefing Plots

### 2024-07-04 minos/outcomes/ChildPovReduction_Combined.Rmd
Added some alternative working directories for priority subgroup and default US runs

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r "inequality_plots", include=FALSE}
# inequality_plots <- function(summary_group, scen.list) {
#   
#   tit <- ' '
#   if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
#   if (summary_group == 'families') { tit <- 'Families' }
#   
#   summary_group <- paste0(summary_group, '_income_quint')
#   
#   data <- do.call(rbind, generate_df_list(summary_group, scen.list))
#   
#   data$income_quintile <- factor(data$income_quintile)
#   
#   # Combine the data
#   data_combined <- data %>%
#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention'))
#   
#   p1 <- ggplot(data_combined, aes(x = year, y = SF_12, group = interaction(income_quintile, scenario), color = income_quintile, linetype = scenario)) +
#     geom_smooth(alpha = 0.7) +
#     scale_color_manual(name = "Income Quintile", 
#                        values = c("red", "blue", "green", "orange", "purple")) +
#     scale_linetype_manual(name = "Scenario", 
#                           values = c("Baseline" = "solid", "Intervention" = "dotted")) +
#     labs(title = "SF_12 Scores by Income Quintile",
#          subtitle = tit,
#          x = "Year",
#          y = "Mean SF_12 MCS") +
#     theme_minimal() +
#     theme(legend.position = "right",
#           legend.title = element_text(size = 12),
#           legend.text = element_text(size = 10))
#   
#   # Aggregate data
#   agg_data <- data %>%
#     mutate(scenario = ifelse(scen == 'baseline', 'Baseline', 'Intervention')) %>%
#     group_by(year, income_quintile, scenario) %>%
#     summarize(mean_SF_12 = mean(SF_12, na.rm = TRUE)) %>%
#     spread(scenario, mean_SF_12) %>%
#     mutate(difference = Intervention - Baseline)
#   
#   p2 <- ggplot(agg_data, aes(x = year, y = difference, fill = income_quintile)) +
#     geom_bar(stat = "identity", position = "dodge") +
#     scale_fill_manual(name = "Income Quintile", 
#                       values = c("red", "blue", "green", "orange", "purple")) +
#     labs(title = "Average Difference in SF_12 Scores by Income Quintile",
#          subtitle = tit,
#          x = "Year",
#          y = "Difference in SF_12 Score") +
#     theme_minimal() +
#     theme(legend.position = "right",
#           legend.title = element_text(size = 12),
#           legend.text = element_text(size = 10))
#   
#   print(p1)
#   print(p2)
# }

inequality_plots <- function(summary_group, scen) {

@@

```{r "Data", include=FALSE}
scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.rel <- 'ChildPovertyReductionRELATIVE_2'
scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
scen.abs <- 'ChildPovertyReductionABSOLUTE'
```

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/psub/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/default_US/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r "inequality_plots", include=FALSE}
inequality_plots <- function(summary_group, scen) {

@@

```{r "Data", include=FALSE}
scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
scen.rel <- 'ChildPovertyReductionRELATIVE_2'
scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE')
scen.abs <- 'ChildPovertyReductionABSOLUTE'
# scen.list.rel <- c('baseline', 'ChildPovertyReductionRELATIVE_psub')
# scen.rel <- 'ChildPovertyReductionRELATIVE_psub'
# scen.list.abs <- c('baseline', 'ChildPovertyReductionABSOLUTE_psub')
# scen.abs <- 'ChildPovertyReductionABSOLUTE_psub'
```
